---
output:
  rmarkdown::github_document:
    html_preview: no
---

<!--- README.md is generated from README.Rmd. Please edit that file -->

## whatdata: Import and export management action data

[![lifecycle](https://img.shields.io/badge/Lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/experimental)
[![R-CMD-check-Ubuntu](https://img.shields.io/github/workflow/status/NCC-CNC/whatdata/Ubuntu/master.svg?label=Ubuntu)](https://github.com/NCC-CNC/whatdata/actions)
[![R-CMD-check-Windows](https://img.shields.io/github/workflow/status/NCC-CNC/whatdata/Windows/master.svg?label=Windows)](https://github.com/NCC-CNC/whatdata/actions)
[![R-CMD-check-Mac-OSX](https://img.shields.io/github/workflow/status/NCC-CNC/whatdata/Mac%20OSX/master.svg?label=Mac%20OSX)](https://github.com/NCC-CNC/whatdata/actions)
[![Coverage Status](https://codecov.io/github/NCC-CNC/whatdata/coverage.svg?branch=master)](https://codecov.io/github/NCC-CNC/whatdata?branch=master)

```{r, include = FALSE}
devtools::load_all()
```

### Overview

The _whatdata R_ package provides functions for importing and exporting management action data. It provides consistent data format standards for the [What To Do](https://github/NCC-CNC/whattodo) and [What Template Maker](https://github/NCC-CNC/whattemplatemaker) web applications. It is not designed for general purpose use outside of these applications.

### Installation

The package is only available from an [online coding repository](https://github.com/NCC-CNC/whatdata). To install it, use the following R code.

```{r, eval = FALSE}
if (!require(devtools))
  install.packages("devtools")
devtools::install_github("NCC-CNC/whatdata")
```
